Spin canonical divisors of log stacky curves

### 2015-07-02 stacky_write_up/spin_cring.tex
read section 7

\begin{defn}
\label{defn:monomial-degree}
Let $k[x_1$, $\ldots$, $x_n]$ be a graded polynomial
ring with $\deg x_i = d_i$ and let $\alpha := \prod_{i = 1}^{n} x_{i}^{f_i} \in
k[x_{1}$, $\ldots$, $x_{n}]$ be a monomial. Then
we define the {\bf degree} of $\alpha$ to be
\[
	\deg \alpha := \sum_{i = 1}^{n} d_i f_i.
\]
\end{defn}

\begin{defn}
\label{defn:grlex}
The {\bf graded lexicographic} order, or {\bf grlex} $\prec_{\text{grlex}}$ on a polynomial ring $k[x_{1}, \ldots,
x_{n}]$ with $\deg x_i = d_i$ is defined as follows.
If $\alpha := \prod_{i = 1}^{n} x_{i}
^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{i}^{f_i'}$ are
monomials in $k[x_{1}$, $\ldots$, $x_{n}]$, then $\alpha
\succ_{\text{grlex}} \beta$ if either $\alpha$ has larger degree:

@@

\begin{defn}
\label{defn:grevlex}
The {\bf graded reverse lexicographic order}, or {\bf grevlex} $\prec_{\text{grevlex}}$ is defined as follows.
If $\alpha := \prod_{i = 1}^{n} x_{i}
^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{i}^{f_i'}$ are
monomials in $k[x_{1}$, $\ldots$, $x_{n}]$, then $\alpha
\succ_{\text{grevlex}} \beta$ if either

@@

Our inductive arguments in Section ~\ref{sec:induction} will
usually have an inclusion $R \supseteq R'$ of log spin canonical
rings such that $R_\halfcan$ is generated by elements $x_{i}$ and $R$
is generated over $R_{\halfcan'}$ by elements $y_j$. In these cases, it is
natural to consider term orders which treat these sets of variables
separately.

\begin{defn}
\label{defn:block-order}
The \textbf{block term order} is defined as follows. Let $k[y_{1}, \ldots, y_{m}]$ and $k[x_{1}, \ldots,
x_{n}]$ be weighted polynomial rings with $\deg y_i = c_i,\: \deg x_i = d_i.$ Further assume we are given existing term
orders $\prec_y$ and $\prec_x$. Let $\alpha :=
\prod_{j = 1}^{m} y_{j}^{h_i}$ $\prod_{i = 1}^{n} x_{i}
^{f_i}$ and $\beta := \prod_{j = 1}^{m} y_{j}^{h_i'}
\prod_{i = 1}^{n} x_{i}^{f_i'}$ be monomials in $k[y_{1},
\ldots, y_{m}] \otimes$ $k[x_{1}, \ldots, x_{n}]$.
Let $\alpha_y := \prod_{j = 1}^{m} y_{j}^{h_i}$ be the
part of $\alpha$ in $k[y_{1}, \ldots, y_{m}]$ and
likewise with $\alpha_x$, $\beta_y$, and $\beta_x$.

@@

\begin{defn}
\label{defn:initial-term}
Let $\prec$ be an ordering on $k[x_{1}$, $\ldots$, $x_{n}],$ with $\deg x_i = d_i$ and let $f \in k[x_{1}, \ldots, x_{n}]$ be a homogeneous
polynomial. The \textbf{initial term} $\initial(f)$ of $f$
is the largest monomial in the support of $f$ with respect to
the ordering $\prec$. Furthermore, we set $\initial(0) := 0$.
\end{defn}

\begin{defn}
\label{defn:initial-ideal}
Let $I$ be a homogeneous ideal of $k[x_{1}$, $\ldots$,
$x_{n}]$. Then the {\bf initial ideal} $\initial(I)$ of $I$ is
the ideal generated by the initial terms of homogeneous polynomials
in $I$:
\[
	\initial(I) := \langle \initial(f) \rangle_{f \in I}
\]
\end{defn}

@@

\begin{defn}
\label{defn:grobner-basis}
Let $I$ be a homogeneous ideal of $k[x_{1}$, $\ldots$,
$x_{n}]$. A \textbf{Gr\"obner basis} for $I$, also known as a
\textbf{standard basis} for $I$, is a set of elements in $I$
such that their initial terms generate the initial
ideal of $I$.
\end{defn}

@@

Using Equation ~\ref{eqn:c-from-lower-terms}, we recursively define a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$. Define 
\[
	S_0 = \{u^l : l \in \BN_{\ge 0}\}
\]
and for each $i \in \BN$, suppose $c_j$ is the maximal element among of $c_1, \ldots c_n$ such that $c_j \le i.$ Note that such a $c_j$ exists because $1=c_1\le i.$ Define
\[
	S_i = y_j \cdot S_{i-j}.
\]
Since each $y_j$ has pole order $c_j$, this recursive construction ensures that 
\[
	z\in S_i \implies -\ord_P^{\halfcan'}(z)=i.
\]
Then define 
\begin{equation}\label{eqn:sat-1-defining-S}
	S = \cup_{i=1}^{\infty} S_i.  
\end{equation}
Note that $S_0$ is not part of this union and in fact $S\cap S_0 = \emptyset$ by pole order considerations.

@@

{\bf Part (b):}
Let $S$ be as defined in Equation \ref{eqn:sat-1-defining-S}, define $U_i$ and $V$ as in the lemma's statement, and set
\[
	T = \left(\bigcup_{i=1}^{n-1} U_i \right) \cup V.
\]

@@

It only remains to check condition (3) of Lemma ~\ref{lem:relations_from_generators_induction}. To do this, suppose $f\in k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ is a monomial not contained in $k[u, x_1, \ldots, x_m]$, meaning there is some $j$ such that $y_j|f$.  Further suppose $f\not\in \langle V \rangle$, meaning that for each $i\in \{1, \ldots m\}$, $x_iy_j \nmid f$. Since $y_j \mid f$ but $x_iy_j \nmid f$, we obtain $x_i\nmid f$.  Therefore, $f\in k[u, y_1, \ldots, y_n]$.  We note that $S$ generates $y_j \cdot (k[u,y_1, \ldots, y_n])$ as a $k$-algebra.  That is, all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
\[
	k[u, x_1, \ldots, x_m] \cup V \cup \left(\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]\right). 
\]
Notice that $S$ generates the ideal $(y_1, \ldots, y_n)$ considered as an ideal of the subring $k[u, y_1, \ldots, y_n]$.  If $f\in S$, then $f=u^b \prod_{j=1}^n {y_j}^{a_j}$. Let $l$ be maximal such that $a_l\ne 0$.
Fix $i \in \{1, \ldots, n\}$. If $y_i \cdot f \notin S$, define
$$
b_j = \begin{cases}
	a_j &\text{ if } j \neq i\\
	a_j + 1 &\text{ if } j=i.
\end{cases}$$

\noindent
Then, there is some $h \in \BN$ such that $i\le h\le \max(i,l)$ satisfying $\prod_{j=1}^h y_j^{b_j}\not\in S$, 
and for all $r<h$ we have $\prod_{j=1}^r {y_j}^{b_j}\in S$.  
Choose some tuple $(\gamma_1, \ldots, \gamma_n)$ which is minimal, in the sense that we cannot decrease any $\gamma_j$ 
and have the following still satisfied: each $\gamma_j\le b_j$ 
and $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S.$ Our recursive definition of 
$S$ and the fact that $\prod_{j=1}^r {y_j}^{b_j}\in S$ implies that for each $1\le r< h$, we have $\prod_{j=1}^r {y_j}^{\gamma_j}\in S$.

We now check that $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$, by checking conditions (*), (**), and (***).  Since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among pole orders of the $y_i$'s) such that $c_h \le \sum_{j=1}^h b_jc_j$ (otherwise, it would be in $S$), which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$, giving us condition (*).  Our choice of $(\gamma_1, \ldots, \gamma_n)$ to be minimal above implies (**).  Since for each $r<h$, we have $\prod_{j=1}^r y_{j}^{a_j}\in S$, condition (***) holds.  Thus $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$.

\todo{how to avoid polynomials hangining over lines like this, ask david} Since the ideal in $k[u, y_1,\ldots, y_n]$ generated by is $S$ is $(y_1, \ldots, y_n) \cdot k[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
\begin{align*}
				& k[u, x_1, \ldots, x_m] \cup \langle V \rangle \cup S \cup \left\langle \bigcup_{i=1}^{n-1} U_i \right\rangle \\
	\subseteq \; 	& S \cup \langle T\rangle \cup \initial(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[u, x_1, \ldots, x_m].
\end{align*}
This shows condition (3) of Lemma ~\ref{lem:relations_from_generators_induction} holds.  Thus, the conditions of 
Lemma ~\ref{lem:relations_from_generators_induction} are met. Finally, Lemma ~\ref{lem:relations_from_generators_induction} implies part (b).  \todo{Peter: Checking that all the conditions of Lemma \ref{lem:relations_from_generators_induction}(2) are met takes a lot of space and clutter.  On the other hand, it is somewhat important.  Should it be included?}

@@

There are two main cases: when $\delta \geq 2$ and when $\delta = 0$,
where we are implicitly appealing to Remark ~\ref{rem:delta-not-1}.
In the first case, $\deg \lfloor \halfcan \rfloor \geq 0$ so the
result directly follows from Lemma ~\ref{lem:sat-1}. When $\delta =
0$, the proof is a rather involved induction using Lemma
~\ref{lem:sat-3} and Lemma ~\ref{lem:raise-stacky-order}. The
remainder of this section is dedicated to characterizing the
saturations ( Subsection ~\ref{ssec:g_0_saturation}), inductive
base cases ( Subsection ~\ref{ssec:g_0_base}), and exceptional
cases (Subsection ~\ref{ssec:g-0-exceptional}) when $\delta = 0$
before proving the main theorem in full for all $\delta$ in
Subsection ~\ref{ssec:g-0-main}.

@@

\ssec{Saturation}
\label{ssec:g_0_saturation}
First, we present the saturations of the canonical divisor for
all cases where $g = 0$ and $\delta = 0,$ as defined in Definition
~\ref{defn:sat}. The saturations can be computed using Riemann-Roch.
By classifying the saturations of all signatures, we can determine
the base cases on which we can apply inductive lemmas from
Section ~\ref{sec:induction}. Exceptional cases are listed first
and generic cases follow.

@@

\ssec{Base Cases}
\label{ssec:g_0_base}
In order to apply Lemma ~\ref{lem:sat-3} and Lemma
~\ref{lem:raise-stacky-order} when $\delta = 0$,
we need to determine appropriate base cases that will
cover all but finitely many signatures by induction.
Here we provide such base cases and demonstrate that
they satisfy all of the necessary conditions of
Lemma ~\ref{lem:sat-3} and Lemma ~\ref{lem:raise-stacky-order}
(e.g. admissibility). We also show that that the associated spin
canonical rings are generated in degree at most $e := \max(5, e_1,
\ldots, e_r)$ with relations generated in degree at most $2e$.

\begin{lem}
\label{lem:g-0-admissible-cases}
Let $(\sx', \Delta, \halfcan')$ be a log spin curve so that $\sx$
has signature $\sigma = (0; e_1, \ldots, e_r; 0)$. Then, $R' := R(
\sx', \Delta, \halfcan')$ has a presentation generated as a $k$-
algebra by elements of degree at most $e = \max(5 , e_1, \ldots, e_r
)$ with relations in degree at most $2e$ and $(\sx ', \halfcan', J)
= (\sx ', -\infty + \sum_{i = 1}^{r} \subhalf{e_i} P_i, J)$ is
admissible for the following cases:

@@

\begin{proof}
Recall that Case (b) is proven in Example ~\ref{eg:base-0-377}. For
the remaining cases, we can use a similar method to find a
presentation satisfying the desired conditions.

The following table demonstrates that $R(\sx', 0, L')$ is
generated as a $k$-algebra by elements of degree at most $e$
with relations in degree at most $2e$ for each case. Also note
that in these cases, $e_i = e + 2 > \deg z$ for all $i \in J$
and any generator $z$ of $R'$.
\begin{longtable}
	{| c || c | c | c |}
	\hline
	Case & Generator Degrees & Degrees of Relations & $e$\\
	\hline
	\hline

@@

	\caption{Genus 0 Non-effective Base Cases Generators/Relations}
	\label{table:g-0-base-cases-degrees}
\end{longtable}

We can also always find a presentation for these cases such that
they satisfy \ref{Ad-i} and \ref{Ad-ii} and that $\initial(I')$ is
generated by products of two monomials. Again, the procedure for
verifying these are similar to that given in Example
~\ref{eg:base-0-377}.

@@

	(c) & $(0; 3, 7, 7; 0)$ & $\{3\}$ & $2$ & $0$ \\ \hline

@@

	\caption{Genus 0 Non-Effective Base Cases \ref{Ad-iii}}
	\label{table:g-0-base-cases-admissibility}
\end{longtable}

@@

Now we can use Lemma ~\ref{lem:sat-3}, Lemma
~\ref{lem:raise-stacky-order}, and Corollary
~\ref{cor:raise-stacky-order} inductively on the cases of Table
~\ref{table:g-0-base-cases} to obtain the desired bounds on the
generator and relation degrees for log spin canonical rings of
genus 0 curves. This process will be carried out in Subsection
~\ref{ssec:g-0-main}.

%Through the application of two inductively adding 
%points via Lemma ~\ref{lem:sat-3} and inductively raising
%stabilizer orders via Lemma ~\ref{lem:raise-stacky-order},
%we obtain Theorem ~\ref{thm:g-0-main} for any
%log spin curve $(\sx, \Delta, L)$ with
%signature $\sigma$ covered by this induction process.
%In particular, this induction process covers all signatures $\sigma
%= (0; e_1, \ldots, e_r; 0)$ such that either $r \geq 5$ or
%for some listed base case $(\sigma', J)$ with $\sigma' = (0; e_1',
%\ldots, e_r'; 0)$, $e_i \geq e_i'$ for all $i$.
%Before we prove the main theorem, we describe the cases not be
%covered by induction.

@@

\noindent
and in particular describe the only exceptions to Theorem ~\ref{thm:main}
in the case $g = 0$.

@@

	\caption{Genus 0 Exceptional Cases}
	\label{table:g-0-exceptional}
\end{longtable}

\begin{rem}
These cases give all of the exceptions to the $e$ and $2e$ bounds on
the generator and relation degree. Notice that each of these
exceptional cases, apart from $(0; 3, 5, 7; 0)$, corresponds to a
signature with saturation not equal to
3, 5, or 9. as seen in Table ~\ref{table:g-0-sat}. Heuristically,
these exceptional saturations can be viewed as ``forcing'' generators
(and thus relations) to lie in higher degrees than expected.
\end{rem}

\ssec{Main Theorem for Genus Zero}
\label{ssec:g-0-main}
Now we can combine this.

@@

\begin{proof}
If $\sx$ has no stacky points, then we can assume that $L \sim
n \cdot \infty$ with $n \in \BZ$. This is the classical
case which is done, with $L$ replaced by $K$, by Voight and
Zureick-Brown ~\cite[Section 4.2]{vzb:stacky}.

First, let us consider the case when $\delta \geq 2$. In any such case,
$\lfloor \halfcan \rfloor$ is an effective divisor and the conditions
of Lemma ~\ref{lem:sat-1} are satisfied. Thus, we can apply
the Lemma ~\ref{lem:sat-1} inductively on the classical case with no stacky points
to get that $R(\sx, \Delta, \halfcan)$ is generated up to degree $e$
with relations generated up to degree $2e$.

By Remark ~\ref{rem:delta-not-1}, it only remains to deal with the case $\delta = 0$, so $\halfcan$ is not effective.
Let $\sigma = (0; e_1, \ldots, e_r; 0)$ be a signature with $r > 0$
so that $\sigma$ is not one of the exceptional cases in Table
~\ref{table:g-0-exceptional}. Note that if $r < 3$, then $\deg 
\lfloor d \halfcan \rfloor < 0$ for all $d \geq 0$ so we have the
trivial case where $R(\sx, \Delta, \halfcan) = k$. Thus, we now
only consider the cases with $r \geq 3$.

>>>>

\begin{defn}
\label{defn:monomial-degree}
Let $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$ be a graded polynomial
ring and let $\alpha := \prod_{i = 1}^{n} x_{d_i, i}^{f_i} \in
k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$ be a monomial. Then
we define the {\bf degree} of $\alpha$ to be
\[
	\deg \alpha := \sum_{i = 1}^{n} d_i f_i.
\]
\end{defn}

\begin{defn}
\label{defn:grlex}
The {\bf graded lexicographic} order, or {\bf grlex} $\prec_{\text{grlex}}$ on a polynomial ring $k[x_{d_1, 1}, \ldots,
x_{d_n, n}]$ is defined as follows.
If $\alpha := \prod_{i = 1}^{n} x_{d_i, i}
^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{d_i, i}^{f_i'}$ are
monomials in $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$, then $\alpha
\succ_{\text{grlex}} \beta$ if either $\alpha$ has larger degree:

@@

\begin{defn}
\label{defn:grevlex}
The {\bf graded reverse lexicographic order}, or {\bf grevlex} $\prec_{\text{grevlex}}$ is defined as follows.
If $\alpha := \prod_{i = 1}^{n} x_{d_i, i}
^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{d_i, i}^{f_i'}$ are
monomials in $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$, then $\alpha
\succ_{\text{grevlex}} \beta$ if either

@@

Our inductive arguments in Section ~\ref{sec:induction} will
usually have an inclusion $R \supseteq R'$ of log spin canonical
rings such that $R_\halfcan$ is generated by elements $x_{d_i, i}$ \todo{They're usually $x_{i,e_i}$ with the degree in the second position, which is a bit strange. Somehow, I think we might want to switch the ordering here, though it still might be confusing.} and $R$
is generated over $R_{\halfcan'}$ by elements $y_j$. In these cases, it is
natural to consider term orders which treat these sets of variables
separately.

\begin{defn}
\label{defn:block-order}
Following Voight and Zureick-Brown \cite[Section 8.1]{vzb:stacky}.
the \textbf{block term order} is defined as follows. Let $k[y_{c_1, 1}, \ldots, y_{c_m, m}]$ and $k[x_{d_1, 1}, \ldots,
x_{d_n, n}]$ be weighted polynomial rings with existing term
orders $\prec_y$ and $\prec_x$, respectively. Let $\alpha :=
\prod_{j = 1}^{m} y_{c_j, j}^{h_i}$ $\prod_{i = 1}^{n} x_{d_i, i}
^{f_i}$ and $\beta := \prod_{j = 1}^{m} y_{c_j, j}^{h_i'}
\prod_{i = 1}^{n} x_{d_i, i}^{f_i'}$ be monomials in $k[y_{d_1', 1},
\ldots, y_{d_m', m}] \otimes$ $k[x_{d_1, 1}, \ldots, x_{d_n, n}]$.
Let $\alpha_y := \prod_{j = 1}^{m} y_{c_j, j}^{h_i}$ be the
part of $\alpha$ in $k[y_{c_1, 1}, \ldots, y_{c_m, m}]$ and
likewise with $\alpha_x$, $\beta_y$, and $\beta_x$.

@@

\begin{defn}
\label{defn:initial-term}
Let $\prec$ be an ordering on $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$ and let $f \in k[x_{d_1, 1}, \ldots, x_{d_n, n}]$ be a homogeneous
polynomial. The \textbf{initial term} $\initial(f)$ of $f$
is the largest monomial in the support of $f$ with respect to
the ordering $\prec$. Furthermore, we set $\initial(0) := 0$.
\end{defn}

\begin{defn}
\label{defn:initial-ideal}
Let $I$ be a homogeneous ideal of $k[x_{d_1, 1}$, $\ldots$,
$x_{d_n, n}]$. Then the {\bf initial ideal} $\initial(I)$ of $I$ is
the ideal generated by the initial terms of homogeneous polynomials
in $I$:
\[
	\initial(I) := \langle \initial(f) \rangle_{f \in I}
\]
\end{defn}

@@

\begin{defn}
\label{defn:grobner-basis}
Let $I$ be a homogeneous ideal of $k[x_{d_1, 1}$, $\ldots$,
$x_{d_n, n}]$. A \textbf{Gr\"obner basis} for $I$, also known as a
\textbf{standard basis} for $I$, is a set of elements in $I$
such that their initial terms generate the initial
ideal of $I$.
\end{defn}

@@

Using Equation ~\ref{eqn:c-from-lower-terms}, we recursively define a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$. Define 
\[
	S_0 = \{u^l : l \in \BN_{\ge 0}\}
\]
and for each $i \in \BN$, suppose $c_j$ is the maximal element among of $c_1, \ldots c_n$ such that $c_j \le i.$ Note that such a $c_j$ exists because $1=c_1\le i.$ Define
\[
	S_i = y_j S_{i-j}.
\]
Since each $y_j$ has pole order $c_j$, this recursive construction ensures that 
\[
	z\in S_i \implies -\ord_P^{\halfcan'}(z)=i.
\]
Then define 
\begin{equation}\label{eqn:sat-1-defining-S}
	S = \cup_{i=1}^{\infty} S_i.  
\end{equation}
Note that $S_0$ is not part of this union and in fact $S\cap S_0 = \emptyset$ by pole order considerations.

@@

{\bf Part (b):}
Let $S$ be as above in Equation \ref{eqn:sat-1-defining-S}, define $U_i$ and $V$ as in the lemma's statement, and set
\[
	T = \left(\bigcup_{i=1}^{n-1} U_i \right) \cup V.
\]

@@

It only remains to check condition (3) of Lemma ~\ref{lem:relations_from_generators_induction}. To do this, suppose $f\in k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ is a monomial not contained in $k[u, x_1, \ldots, x_m]$, meaning there is some $j$ such that $y_j|f$.  Further suppose $f\not\in \langle V \rangle$, meaning that for each $i\in \{1, \ldots m\}$, $x_iy_j \nmid f$. Since $y_j \mid f$ but $x_iy_j \nmid f$, we obtain $x_i\nmid f$.  Therefore, $f\in k[u, y_1, \ldots, y_n]$.  We note that $S$ generates $y_j \cdot (k[u,y_1, \ldots, y_n])$ as a $k$-algebra.  That is, all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
\[
	k[u, x_1, \ldots, x_m] \cup V \cup \left(\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]\right). 
\]
Notice that $S$ generates the ideal $\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]$.  If $f\in S$, then $f=u^b \prod_{j=1}^n {y_j}^{a_j}$; let $l$ be maximal such that $a_l\ne 0$.
If $i\in \{1, \ldots, n\}$, then $y_i f$ is either in $S$ or there is some $h \in \BN$ such that $i\le h\le \max(i,l)$ satisfying $\prod_{j=1}^h y_j^{b_j}\not\in S$, 
and for all $r<h$ $\prod_{j=1}^r {y_j}^{b_j}\in S$, where $b_j=a_j$ when $j\ne i$ and $b_i=a_i+1$.  Choose $(\gamma_1, \ldots, \gamma_n)$ minimal (that is, so that we cannot decrease any $\gamma_j$ and have the following still satisfied) such that each $\gamma_j\le b_j$ and $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S$; our recursive definition of $S$ implies that for each $1\le r< h$, we still have $\prod_{j=1}^r {y_j}^{\gamma_j}\in S$.

We now check that $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$, by checking conditions (*), (**), and (***).  Since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among pole orders of the $y_i$s) such that $c_h \le \sum_{j=1}^h b_jc_j$ (otherwise, it would be in $S$), which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$, giving us condition (*).  Our choice of $(\gamma_1, \ldots, \gamma_n)$ to be minimal above immediately gives (**).  Since for each $r<h$, $\prod_{j=1}^r y_{j}^{a_j}\in S$, we get condition (***).  Thus $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$.

Since $S$ generates $\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
\begin{align*}
				& k[u, x_1, \ldots, x_m] \cup \langle V \rangle \cup S \cup \left\langle \bigcup_{i=1}^{n-1} U_i \right\rangle \\
	\subseteq \; 	& S \cup \langle T\rangle \cup \initial(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[u, x_1, \ldots, x_m].
\end{align*}
This shows condition (3) of Lemma ~\ref{lem:relations_from_generators_induction} holds.  Thus, the conditions of 
Lemma ~\ref{lem:relations_from_generators_induction} are met. Finally, Lemma ~\ref{lem:relations_from_generators_induction} implies part (b).  \todo{Peter: Checking that all the conditions of Lemma \ref{lem:relations_from_generators_induction}(2) are met takes a lot of space and clutter.  On the other hand, it is somewhat important.  Should it be included?}

@@

As noted in Remark ~\ref{rem:delta-not-1}, $\delta$ is even, so we can reduce to two cases: $\delta \geq 2$ and $\delta = 0$.
In the former case, $\halfcan$ is linearly equivalent to an effective divisor, so the
result of Theorem \ref{thm:main} follows immediately by repeatedly applying Lemma ~\ref{lem:sat-1} to add the necessary fractional points.
On the other hand, the proof when $\delta =
0$ is a more involved, and we dedicate the remainder of this section to proving it through the following steps: 
characterizing saturations points (Subsection ~\ref{ssec:g_0_saturation}), describing
base cases (Subsection ~\ref{ssec:g_0_base}), presenting exceptional
cases (Subsection ~\ref{ssec:g-0-exceptional}), and applying inductive Lemmas ~\ref{lem:sat-3} and ~\ref{lem:raise-stacky-order} to prove\todo{synonym for prove, so its not repeated twice in this sentence?} Theorem \ref{thm:main} when $\delta = 0$ (Subsection ~\ref{ssec:g-0-main}.\todo{Peter: I made some changes to this last paragraph (gramatical and stylistic-not mathematical).  See if you like them.}
%before proving the main theorem in full for all $\delta$ in
%Subsection ~\ref{ssec:g-0-main}.

@@

\ssec{Saturation}
\label{ssec:g_0_saturation}
First, we present the saturations, as defined in Definition
~\ref{defn:sat}, of the canonical divisor for
all cases where $g = 0$ and $\delta = 0$. The saturations can be computed using Riemann-Roch.
By classifying the saturations of all signatures, we can determine
the base cases on which we can apply inductive lemmas from
Section ~\ref{sec:induction}. Exceptional cases are listed first
and generic cases follow.

@@

\ssec{Base Cases}
\label{ssec:g_0_base}
In order to apply Lemma ~\ref{lem:sat-3} and Lemma
~\ref{lem:raise-stacky-order} when $\delta = 0$,
we need to determine appropriate base cases that will
cover all but finitely many signatures by induction.
Here we provide such base cases and demonstrate that
they satisfy all of the necessary conditions of
Lemma ~\ref{lem:sat-3} and Lemma ~\ref{lem:raise-stacky-order}
(e.g. admissibility as defined in Definition \ref{defn:admissible}). We also show that that the associated spin
canonical rings are generated in degree at most $e := \max(5, e_1,
\ldots, e_r)$ with relations generated in degree at most $2e$.

\begin{lem}
\label{lem:g-0-admissible-cases}
Let $(\sx', \Delta, \halfcan')$ be a log spin curve with signature $(0; e_1, \ldots, e_r; 0)$. Then, $R' := R_{\halfcan'}$ is generated by elements of degree at most $e = \max(5 , e_1, \ldots, e_r
)$ with relations in degree at most $2e$ and $(\sx ', \halfcan', J)
= (\sx ', -\infty + \sum_{i = 1}^{r} \subhalf{e_i} P_i, J)$ is
admissible in the following cases:

@@

\begin{proof}
Recall that Case (b) is proven in Example ~\ref{eg:base-0-377}. For
the remaining cases, we one follow a similar method to find a
presentation satisfying the desired conditions.

The following table demonstrates \todo{Peter: Demonstrates maybe isn't the right word.  Really the table states it, but we want to find a better word than that.} that $R(\sx', 0, L')$ is
generated as a $k$-algebra by elements of degree at most $e$
with relations in degree at most $2e$ for each case. Also note
that in these cases, $e_i = e + 2 > \deg z$ for all $i \in J$
and any generator $z$ of $R'$.
\begin{longtable}
	{| c || c | c | c |}
	\hline
	Case & Generator Degrees & Degrees of Relations & $e$\\
	\hline
	\hline

@@

	\caption{Genus 0 Non-effective Base Cases Generators/Relations}
	\label{table:g-0-base-cases-degrees}
\end{longtable}
\todo{Peter: Can we make a better description for the table above?}

We can also always find a presentation for these cases such that
they satisfy \ref{Ad-i} and \ref{Ad-ii} and that $\initial(I')$ is
generated by products of two monomials. Again, the procedure to
verify these is similar to that in Example
~\ref{eg:base-0-377}.

@@

	(c) & $(0; 3, 7, 7; 0)$ & $\{2, 3\}$ & $2$ & $0$ \\ \hline

@@

	\caption{Genus 0 Non-Effective Base Cases \ref{Ad-iii}}
	\label{table:g-0-base-cases-admissibility}
\end{longtable}
\todo{Peter: In case c, I changed $J=\{3\}$ to $J=\{2, 3\}$.}
\todo{Peter: I don't particularly like split tables.  Might we consider not using [h], so its not split}

@@

Now we can use Lemma ~\ref{lem:sat-3}, Lemma
~\ref{lem:raise-stacky-order}, and Corollary
~\ref{cor:raise-stacky-order} to induct from the cases of Table
~\ref{table:g-0-base-cases} and obtain the desired bounds on the
generator and relation degrees for log spin canonical rings of
genus 0 curves. This process will be carried out in Subsection
~\ref{ssec:g-0-main}.
\todo{Peter: I don't think this paragraph should be here.  It seems like its kind of redundant given section 7.4.  Maybe, we could just, say something like ``these provide the base cases, from which we will induct in section 7.4.''}
%Through the application of two inductively adding 
%points via Lemma ~\ref{lem:sat-3} and inductively raising
%stabilizer orders via Lemma ~\ref{lem:raise-stacky-order},
%we obtain Theorem ~\ref{thm:g-0-main} for any
%log spin curve $(\sx, \Delta, L)$ with
%signature $\sigma$ covered by this induction process.
%In particular, this induction process covers all signatures $\sigma
%= (0; e_1, \ldots, e_r; 0)$ such that either $r \geq 5$ or
%for some listed base case $(\sigma', J)$ with $\sigma' = (0; e_1',
%\ldots, e_r'; 0)$, $e_i \geq e_i'$ for all $i$.
%Before we prove the main theorem, we describe the cases not be
%covered by induction.

@@

\noindent
and in particular describe the only exceptions to Theorem ~\ref{thm:main}
in the case $g = 0$.  \todo{This paragraph is kind of repetitive, and awkward.}

@@

	\caption{Genus 0 Exceptional Cases}
	\label{table:g-0-exceptional}
\end{longtable}
\todo{Peter: Technically, shouldn't the first and last $e$ be 5 instead of 3, since $e=\max(5, e_i)$?}

\begin{rem}
These cases give all of the exceptions to the $e$ and $2e$ bounds on
the generator and relation degree. Notice that each of these
exceptional cases, apart from $(0; 3, 5, 7; 0)$, has saturation not in $\{3, 5, 9\}$ as seen in Table ~\ref{table:g-0-sat}.
Heuristically, \todo{Peter: Is heuristically the right word here?  I interpret heuristically to mean ``providing a technique or method to solve a problem,'' whereas I think you mean something more along the lines of intuitively.}
these exceptional saturations can be viewed as ``forcing'' generators and relations in higher degrees than expected.
\end{rem}

\ssec{Main Theorem for Genus Zero}
\label{ssec:g-0-main}
Now we can combine the base cases from Subsection \ref{ssec:g_0_base} with the inductive lemmas of Section \ref{sec:induction}.

@@

\begin{proof}
If $\sx$ has no stacky points, then we can assume that $L \sim
n \cdot \infty$ with $n \in \BZ$. This is the classical
case which is done, with $L$ replaced by $K$, \todo{Peter: I don't think its helpful to say with $L$ replaced by $K$.  It might slightly confuse the reader into thinking that replacing half canonical divisor with canonical divisor changes the problem.} by Voight and
Zureick-Brown ~\cite[Section 4.2]{vzb:stacky}.

First, consider the case when $\delta \geq 2$. \todo{Peter: it feels a tiny bit redundant here, as we kind of said this in the introduction to the section.}
 In any such cases,
$\halfcan_X$ is an effective divisor so we can inductively apply
the Lemma ~\ref{lem:sat-1} from the classical non-stacky case
to deduce that $R(\sx, \Delta, \halfcan)$ is generated up to degree $e$
with relations generated up to degree $2e$.

By Remark ~\ref{rem:delta-not-1}, it only remains to deal with the case $\delta = 0$, so $\halfcan_X$ is not effective.
Let $\sigma = (0; e_1, \ldots, e_r; 0)$ not be one of the exceptional cases in Table
~\ref{table:g-0-exceptional}.  We get the following three cases, depending on the value of $r$:

\vskip.1in
\noindent
{\sf Case 1: $r<3$}

If $r < 3$, then $\deg 
\lfloor d \halfcan \rfloor < 0$ for all $d \geq 0$ so we get the
trivial ring $R(\sx, \Delta, \halfcan) = k$.

\vskip.1in
\noindent
{\sf Case 2: $3\le r \le 5$}
